Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-05-13 main.Rmd
changed fig.pos

```{r linear-time, echo=FALSE, fig.cap="(ref:linear-time)", fig.pos="!htb"}
```

@@

```{r allFig, fig.pos="!htb", fig.align= 'left',echo=FALSE, eval=TRUE, warning=FALSE,message = FALSE, fig.cap= "(ref:allFig)", fig.show = 'hold'}
```

@@

```{r bothcust, fig.cap = "(ref:bothcust)", fig.pos="!htb"}
```

>>>>

```{r linear-time, echo=FALSE, fig.cap="(ref:linear-time)", fig.pos="!htbp"}
```

@@

```{r allFig, fig.pos="!p", fig.align= 'left',echo=FALSE, eval=TRUE, warning=FALSE,message = FALSE, fig.cap= "(ref:allFig)", fig.show = 'hold'}
```

@@

```{r bothcust, fig.cap = "(ref:bothcust)", fig.pos="!p"}
```
